My English activity log

### 2020-02-03 _posts/2019-11-04-my-english-activity-log/my-english-activity-log.Rmd
jusqu'au 03/02/2020

>>>>

* **17/12/2019** : I watched a video about study skills and habits https://www.youtube.com/watch?v=jCdTaLI5tVk.

* **19/12/2019**  :I watched a video about Archaea https://www.youtube.com/watch?v=VGcT1-XaWgk.

* **22/12/2019** : I read the 13th chapter of "The Hobbit".

* **29/12/2019** : I read the 14th chapter of "The Hobbit".

# 2020

## January

* **05/01/2020** : I read the 15th chapter of "The Hobbit".

* **26/01/2020** : I read the 16th chapter of "The Hobbit".

* **28/01/2020** : I read the 17th chapter of "The Hobbit".

* **31/01/2020** : I read the 18th chapter of "The Hobbit".

## February

* **02/02/2020** : I read the last chapter of "The Hobbit".
